### 2011-08-10 doc/theses/vitasek/diplomka.tex
Thesis: in progress.

\begin{itemize}
	\item For each input file: how long does model creation take?
	\item How long does it take to communicate with GLPK? Creating the input/parsing the output.
	\item Which construction heuristic is the best - limit GLPK to like 1 second
	\item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
	\item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Alpha, Beta -> How does the solution work?
	\item Which GLPK -> How does (time->quality) look, how does (input->time) look
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Seems that Random is better and even has smaller variance)
\end{itemize}

@@

Results:
Start time: Thu Jan 01 01:22:17 CET 1970
Total time spent: 7754 ms
Final quality: 0.19951219512195123 (10 AMs)
Highest quality: 0.23463414634146343 (12 AMs)
Construction phase: 
  Algorithm: Random
    Time taken: 248 ms
    Time since start: 248 ms
    Pool size: 10
    Quality: 0.19975609756097568 (11 AMs)
Improvement phase: 
  pass #1: 
  Algorithm: RandomRemove, ratio = 0.2
    Time taken: 0 ms
    Time since start: 841 ms
    Pool size: 10
    Quality: 0.15878048780487808 (9 AMs)
  pass #2: 
  Algorithm: Mutation, ratio = 0.1, limit = 1 s
    Time taken: 1512 ms
    Time since start: 2710 ms
    Pool size: 11
    Quality: 0.21975609756097558 (11 AMs)

>>>>

\begin{itemize}
	\item For each input file: how long does model creation take?
	\item How long does it take to communicate with GLPK? Creating the input/parsing the output.
	\item Which construction heuristic is the best - limit GLPK to like 1 second
	\item With the best construction heuristic, which IH is the best? Note that this needn't be the best combination!
	\item With the best IH from the previous step, how about using Random as CH?
	\item GLPK: Input -> How long the search for optimum lasts - this shows we cannot rely on GLPK alone! it just takes too long.
	\item GLPK: Time limit -> Quality
	\item Structure of the data -> Which algorithms perform the best
	\item Alpha, Beta -> Quality
	\item Alpha, Beta -> How does the solution work?
	\item Which GLPK -> How does (time->quality) look, how does (input->time) look
	\item Do I beat FIDAX with Random?
	\item Does Fuzzy beat Random? (Fuzzy wins for every single case) - take note of quality (mean, variance) but also time (again, mean)
\end{itemize}

@@

Results:
Total time spent: 7754 ms
Final quality: 0.19951219512195123 (10 AMs)
Highest quality: 0.23463414634146343 (12 AMs)
Construction phase: 
  Algorithm: Random
    Time taken: 248 ms
    Time since start: 248 ms
    Pool size: 10
    Quality: 0.19975609756097568 (11 AMs)
Improvement phase: 
  pass #1: 
  Algorithm: RandomRemove, ratio = 0.2
    Time taken: 0 ms
    Time since start: 841 ms
    Pool size: 10
    Quality: 0.15878048780487808 (9 AMs)
  pass #2: 
  Algorithm: Mutation, ratio = 0.1, limit = 1 s
    Time taken: 1512 ms
    Time since start: 2710 ms
    Pool size: 11
    Quality: 0.21975609756097558 (11 AMs)
